---
title: "Usage Example"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Usage Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<div style="text-align: justify">

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
install.packages("INLA", repos=c(getOption("repos"), INLA="https://inla.r-inla-download.org/R/stable"), dep=TRUE)
library("dplyr")
library("ggplot2")
```

# Introduction

```{r setup}
library("INLA.SocialEp")
```

# Understanding the inputs

User needs to provide a graph for the function that can be prepared from an sf object like:

```{r}
sec.nb <- spdep::poly2nb(sp_object_sim, snap=0.0000005)
spdep::nb2INLA("MapGraph", sec.nb)
graph_states <- INLA::inla.read.graph("MapGraph")
```

Moreover, the user needs to provide the data with a data.frame that has the following structure:

  * **obs**: contains the observations for the response variable per area and group.
  * **exp**: contains the expected values per area and group.
  * **lev.fac1**: contains the levels of *factor 1* per area and group.
  * **lev.fac2**: contains the levels of *factor 2* per area and group.

```{r}
data_mod <- data.frame(
  "obs" = c(sp_object_sim$OBS_M6_SIM_G1_v3, sp_object_sim$OBS_M6_SIM_G2_v3, 
            sp_object_sim$OBS_M6_SIM_G3_v3, sp_object_sim$OBS_M6_SIM_G4_v3),
  "exp" = c(sp_object_sim$EXP, sp_object_sim$EXP, sp_object_sim$EXP, sp_object_sim$EXP),
  "lev.fac1" = c(rep("F1L1", graph_states$n*2), rep("F1L2", graph_states$n*2)), 
  "lev.fac2" = c(rep("F2L1", graph_states$n), rep("F2L2", graph_states$n), rep("F2L1", graph_states$n), rep("F2L2", graph_states$n))
)
```

# Customizing parameters

There are three mainly aspects regarding the modelization and post-processing that can be modified by the user:

  * **Prior Specification**: the function allows the user to choose between uniform prior (`sp.prior = "pc.prec"`) or Penalized-Complexity priors (`sp.prior = "pc.prec"`), with the user being able to modify the paremeters of the PC prior using option `pc.prec.val = c(1, 0.01)`.
  * **Shared Copies in INLA**: you can control if you want the shared copies to be fixed with option `sp.copy.fixed=TRUE`.
  * **Scaled Spatial Effects**: this option controls whether the random spatial effects have their variance scaled (`TRUE`) or not (`FALSE`).
  
We can now run the model:

```{r chunk2}
ResMod <- inla.SpANOVA.2x2(
  data = data_mod,
  gr = graph_states,
  fac.names = c("F1", "F2"),
  lev.fac1 = c("F1L1", "F1L2"),
  lev.fac2 = c("F2L1", "F2L2"),
  scale.mod = FALSE,
  sp.prior = "pc.prec",
  pc.prec.val = c(1, 0.01),
  sp.copy.fixed = FALSE,
  save.res=FALSE, 
  save.random=FALSE,
  save.hyper=FALSE, 
  save.mod.data=TRUE
  )
```

After that we can run the function `inla.null.sp()`. In this case, we will set the threshold for considering a spatial effect as spurious if the standard deviation is below $0.125$:

```{r chunk3}
ResMod <- inla.null.sp(ResMod, thres = 0.125)
```

And we can finally check the summary of the results obtained:

```{r chunk4}
ResMod$Summary
```

We can also check the spatial effects adjusted:

```{r chunk5}
plot.SpANOVA(
  obj=ResMod,
  obj_type="SpANOVA",
  fill_by="Spatial",
  n_mod=20,
  sp_object=sp_object_sim,
  breaks=c(-3, -2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3),
  fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
  scale_name="Values",
  sp_null=0.125,
  legend.position="right",
  ncol_fig=2
)
```

As well as the adjusted relative risks:

```{r chunk6}
plot.SpANOVA(
  obj=ResMod,
  obj_type="SpANOVA",
  fill_by="RR",
  n_mod=20,
  sp_object=sp_object_sim,
  breaks=c(0, 0.5, 0.9, 1.1, 2, 3),
  fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
  scale_name="Values",
  sp_null=0.125,
  legend.position="right",
  ncol_fig=2
)
```

***
