---
title: "Usage Example"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Usage Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<div style="text-align: justify">

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
install.packages("INLA", repos=c(getOption("repos"), INLA="https://inla.r-inla-download.org/R/stable"), dep=TRUE)
library("dplyr")
library("ggplot2")
```

# Introduction

```{r}
library("INLA.SocialEp")
```

# Understanding the inputs

User needs to provide a graph for the function that can be prepared from an sf object like:

```{r}
sec.nb <- spdep::poly2nb(sp_object_sim, snap=0.0000005)
spdep::nb2INLA("MapGraph", sec.nb)
graph_states <- INLA::inla.read.graph("MapGraph")
```

Moreover, the user needs to provide the data with a data.frame that has the following structure:

  * **obs**: contains the observations for the response variable per area and group.
  * **exp**: contains the expected values per area and group.
  * **lev.fac1**: contains the levels of *factor 1* per area and group.
  * **lev.fac2**: contains the levels of *factor 2* per area and group.

```{r}
data_mod <- data.frame(
  "obs" = c(sp_object_sim$OBS_M6_SIM_G1_v3, sp_object_sim$OBS_M6_SIM_G2_v3, 
            sp_object_sim$OBS_M6_SIM_G3_v3, sp_object_sim$OBS_M6_SIM_G4_v3),
  "exp" = c(sp_object_sim$EXP, sp_object_sim$EXP, sp_object_sim$EXP, sp_object_sim$EXP),
  "lev.fac1" = c(rep("F1L1", graph_states$n*2), rep("F1L2", graph_states$n*2)), 
  "lev.fac2" = c(rep("F2L1", graph_states$n), rep("F2L2", graph_states$n), rep("F2L1", graph_states$n), rep("F2L2", graph_states$n))
)
```

# Customizing parameters

There are three mainly aspects regarding the modelization and post-processing that can be modified by the user:

  * **Prior Specification**: the function allows the user to choose between uniform prior (`sp.prior = "pc.prec"`) or Penalized-Complexity priors (`sp.prior = "pc.prec"`), with the user being able to modify the paremeters of the PC prior using option `pc.prec.val = c(1, 0.01)`.
  * **Shared Copies in INLA**: you can control if you want the shared copies to be fixed with option `sp.copy.fixed=TRUE`.
  * **Scaled Spatial Effects**: this option controls whether the random spatial effects have their variance scaled (`TRUE`) or not (`FALSE`).
  
We can now run the model:

```{r chunk2}
ResMod <- INLA.SocialEp::inla.SpANOVA.2x2(
  data = data_mod,
  gr = graph_states,
  fac.names = c("F1", "F2"),
  lev.fac1 = c("F1L1", "F1L2"),
  lev.fac2 = c("F2L1", "F2L2"),
  scale.mod = FALSE,
  sp.prior = "pc.prec",
  pc.prec.val = c(1, 0.01),
  sp.copy.fixed = FALSE,
  save.res=FALSE, 
  save.random=FALSE,
  save.hyper=FALSE, 
  save.mod.data=TRUE
  )
```

After that we can run the function `inla.null.sp()`. In this case, we will set the threshold for considering a spatial effect as spurious if the standard deviation is below $0.125$:

```{r chunk3}
ResMod <- INLA.SocialEp::inla.null.sp(ResMod, thres = 0.125)
```

And we can finally check the summary of the results obtained:

```{r chunk4}
ResMod$Summary
```

We can also plot the spatial effects adjusted for each of the models using the function `plot.SpANOVA()``:

```{r include=FALSE}
library("stringr")
library("ggplot2")
library("gridExtra")
convert_col <- function(data,
                        breaks,
                        pal_fun,
                        include.lowest=TRUE,
                        right = TRUE,
                        na.col = NA) {

  if (!is.numeric(breaks) || length(breaks) < 2)
    stop("`breaks` must be a numeric vector with length >= 2.")

  nbins <- length(breaks) - 1
  cols  <- pal_fun(nbins)
  btxt   <- format(breaks, trim = TRUE, scientific = FALSE)
  left   <- head(btxt, -1)
  rightb <- tail(btxt, -1)

  labs <- if (right) {
    paste0("(", left, ",", rightb, "]")
  } else {
    paste0("[", left, ",", rightb, ")")
  }
  labs <- stringr::str_replace_all(labs, "(?<=\\d)\\.0(?=[,\\]])", "")

  data_lab <- if (is.numeric(data)) {
    as.character(base::cut(data, breaks = breaks, right = right, include.lowest = include.lowest))
  } else {
    trimws(as.character(data))
  }

  out <- cols[match(data_lab, labs)]
  out[is.na(data_lab)] <- na.col
  data <- list()
  data[[1]] <- out
  data[[2]] <- labs
  data[[3]] <- cols
  names(data) <- c("fill_by", "tags", "colors")
  data
}


plot.SpANOVA <- function(
    obj,
    obj_type=c("SpANOVA", "INLA"),
    fill_by=c("Spatial", "Heterogeneity", "RR"),
    n_mod,
    sp_object,
    breaks=NA,
    fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
    col_frontiers="black",
    scale_name="Values",
    sp_null=0.125,
    legend.position="right",
    ncol_fig=2
    ){

  # Basic checks
  if(!(fill_by %in% c("Spatial", "Heterogeneity", "RR"))){stop("Please specify a proper fill_by argument.")}
  if(!(obj_type %in% c("SpANOVA", "INLA"))){stop("Please specify a proper object type.")}
  if(length(fil_scale)<2){stop("Please specify at least two colors for the colour scale.")}

  # Prepare breaks
  if(sum(is.na(breaks)) & fill_by %in% c("Spatial", "Heterogeneity")){
    breaks <- c(-5, -2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 5)
  }else if(sum(is.na(breaks)) & fill_by=="RR"){
    breaks <- c(0, 0.5, 0.9, 1.1, 2, Inf)
  }

  # Prepare colour scale
  CScale <- grDevices::colorRampPalette(fil_scale)

  # Retrieve groups
  groups_names <- obj[[n_mod]]$groups
  sp_names <- obj[[n_mod]]$sp_effects

  # Prepare data to plot
  if(obj_type=="SpANOVA"){
    if(fill_by=="Heterogeneity"){
      sp_object$sp1 <- obj[[n_mod]]$summary.random$omega_j$mean[1:nrow(sp_object)]
      sp_object$sp2 <- obj[[n_mod]]$summary.random$omega_j$mean[(nrow(sp_object)+1):(2*nrow(sp_object))]
      sp_object$sp3 <- obj[[n_mod]]$summary.random$omega_j$mean[((2*nrow(sp_object)+1)):(3*nrow(sp_object))]
      sp_object$sp4 <- obj[[n_mod]]$summary.random$omega_j$mean[(3*nrow(sp_object)+1):(4*nrow(sp_object))]
    }else if(fill_by=="RR"){
      sp_object$sp1 <- obj[[n_mod]]$summary.fitted.values$mean[1:nrow(sp_object)]
      sp_object$sp2 <- obj[[n_mod]]$summary.fitted.values$mean[(nrow(sp_object)+1):(2*nrow(sp_object))]
      sp_object$sp3 <- obj[[n_mod]]$summary.fitted.values$mean[((2*nrow(sp_object)+1)):(3*nrow(sp_object))]
      sp_object$sp4 <- obj[[n_mod]]$summary.fitted.values$mean[(3*nrow(sp_object)+1):(4*nrow(sp_object))]
    }else if(fill_by=="Spatial"){
      if(n_mod == 1){
        sp_object$sp1 <- NA
        sp_object$sp2 <- NA
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod == 2){
        sp_object$sp1 <- obj[[n_mod]]$summary.random$phi_1$mean
        sp_object$sp2 <- obj[[n_mod]]$summary.random$phi_2$mean
        sp_object$sp3 <- obj[[n_mod]]$summary.random$phi_3$mean
        sp_object$sp4 <- obj[[n_mod]]$summary.random$phi_4$mean
      }else if(n_mod %in% c(3, 4, 5, 6)){
        sp_object$sp1 <- obj[[n_mod]]$summary.random$phi_11$mean
        sp_object$sp2 <- NA
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(7, 8)){
        sp_object$sp1 <- obj[[n_mod]]$summary.random$phi_11$mean
        sp_object$sp2 <- obj[[n_mod]]$summary.random$phi_21$mean
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(9, 10)){
        sp_object$sp1 <- obj[[n_mod]]$summary.random$phi_11$mean
        sp_object$sp2 <- obj[[n_mod]]$summary.random$phi_12$mean
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(11, 12, 13, 14)){
        sp_object$sp1 <- obj[[n_mod]]$summary.random$phi_11$mean
        sp_object$sp2 <- obj[[n_mod]]$summary.random$phi_12$mean
        sp_object$sp3 <- obj[[n_mod]]$summary.random$phi_21$mean
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(15, 16, 17, 18, 19, 20, 21, 22)){
        sp_object$sp1 <- obj[[n_mod]]$summary.random$phi_11$mean
        sp_object$sp2 <- obj[[n_mod]]$summary.random$phi_12$mean
        sp_object$sp3 <- obj[[n_mod]]$summary.random$phi_21$mean
        sp_object$sp4 <- obj[[n_mod]]$summary.random$phi_22$mean
      }
    }
  }else if(obj_type=="INLA"){
    if(fill_by=="Heterogeneity"){
      sp_object$sp1 <- obj$summary.random$omega_j$mean[1:nrow(sp_object)]
      sp_object$sp2 <- obj$summary.random$omega_j$mean[(nrow(sp_object)+1):(2*nrow(sp_object))]
      sp_object$sp3 <- obj$summary.random$omega_j$mean[((2*nrow(sp_object)+1)):(3*nrow(sp_object))]
      sp_object$sp4 <- obj$summary.random$omega_j$mean[(3*nrow(sp_object)+1):(4*nrow(sp_object))]
    }else if(fill_by=="RR"){
      sp_object$sp1 <- obj$summary.fitted.values$mean[1:nrow(sp_object)]
      sp_object$sp2 <- obj$summary.fitted.values$mean[(nrow(sp_object)+1):(2*nrow(sp_object))]
      sp_object$sp3 <- obj$summary.fitted.values$mean[((2*nrow(sp_object)+1)):(3*nrow(sp_object))]
      sp_object$sp4 <- obj$summary.fitted.values$mean[(3*nrow(sp_object)+1):(4*nrow(sp_object))]
    }else if(fill_by=="Spatial"){
      if(n_mod == 1){
        sp_object$sp1 <- NA
        sp_object$sp2 <- NA
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod == 2){
        sp_object$sp1 <- obj$summary.random$phi_1$mean
        sp_object$sp2 <- obj$summary.random$phi_2$mean
        sp_object$sp3 <- obj$summary.random$phi_3$mean
        sp_object$sp4 <- obj$summary.random$phi_4$mean
      }else if(n_mod %in% c(3, 4, 5, 6)){
        sp_object$sp1 <- obj$summary.random$phi_11$mean
        sp_object$sp2 <- NA
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(7, 8)){
        sp_object$sp1 <- obj$summary.random$phi_11$mean
        sp_object$sp2 <- obj$summary.random$phi_21$mean
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(9, 10)){
        sp_object$sp1 <- obj$summary.random$phi_11$mean
        sp_object$sp2 <- obj$summary.random$phi_12$mean
        sp_object$sp3 <- NA
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(11, 12, 13, 14)){
        sp_object$sp1 <- obj$summary.random$phi_11$mean
        sp_object$sp2 <- obj$summary.random$phi_12$mean
        sp_object$sp3 <- obj$summary.random$phi_21$mean
        sp_object$sp4 <- NA
      }else if(n_mod %in% c(15, 16, 17, 18, 19, 20, 21, 22)){
        sp_object$sp1 <- obj$summary.random$phi_11$mean
        sp_object$sp2 <- obj$summary.random$phi_12$mean
        sp_object$sp3 <- obj$summary.random$phi_21$mean
        sp_object$sp4 <- obj$summary.random$phi_22$mean
      }
    }
  }

  # Estimate standard deviation for each effect
  sd_sp1 <- round(sd(pull(sp_object, sp1)), 2)
  sd_sp2 <- round(sd(pull(sp_object, sp2)), 2)
  sd_sp3 <- round(sd(pull(sp_object, sp3)), 2)
  sd_sp4 <- round(sd(pull(sp_object, sp4)), 2)

  # Create titles
  if(fill_by=="Spatial"){
    if(n_mod == 1){
      title1 <- "No Effect"
      title2 <- "No Effect"
      title3 <- "No Effect"
      title4 <- "No Effect"
    }else if(n_mod == 2){
      title1 <- bquote("Spatial Effect | "~phi[1])
      title2 <- bquote("Spatial Effect | "~phi[2])
      title3 <- bquote("Spatial Effect | "~phi[3])
      title4 <- bquote("Spatial Effect | "~phi[4])
    }else if(n_mod %in% c(3, 4, 5, 6)){
      title1 <- bquote("Spatial Effect | "~phi[11])
      title2 <- "No Effect"
      title3 <- "No Effect"
      title4 <- "No Effect"
    }else if(n_mod %in% c(7, 8)){
      title1 <- bquote("Spatial Effect | "~phi[11])
      title2 <- bquote("Spatial Effect | "~phi[12])
      title3 <- "No Effect"
      title4 <- "No Effect"
    }else if(n_mod %in% c(9, 10)){
      title1 <- bquote("Spatial Effect | "~phi[11])
      title2 <- bquote("Spatial Effect | "~phi[21])
      title3 <- "No Effect"
      title4 <- "No Effect"
    }else if(n_mod %in% c(11, 12, 13, 14)){
      title1 <- bquote("Spatial Effect | "~phi[11])
      title2 <- bquote("Spatial Effect | "~phi[12])
      title3 <- bquote("Spatial Effect | "~phi[21])
      title4 <- "No Effect"
    }else if(n_mod %in% c(15, 16, 17, 18, 19, 20, 21, 22)){
      title1 <- bquote("Spatial Effect | "~phi[11])
      title2 <- bquote("Spatial Effect | "~phi[12])
      title3 <- bquote("Spatial Effect | "~phi[21])
      title4 <- bquote("Spatial Effect | "~phi[22])
    }
  }else if(fill_by=="RR"){
    title1 <- paste0("Relative Risk Adjusted | G1")
    title2 <- paste0("Relative Risk Adjusted | G2")
    title3 <- paste0("Relative Risk Adjusted | G3")
    title4 <- paste0("Relative Risk Adjusted | G4")
  }else if(fill_by=="Heterogeneity"){
    title1 <- bquote("Heterogeneity Effect | "~omega[1])
    title2 <- bquote("Heterogeneity Effect | "~omega[2])
    title3 <- bquote("Heterogeneity Effect | "~omega[3])
    title4 <- bquote("Heterogeneity Effect | "~omega[4])
  }

  # Prepare Figures
  if(fill_by %in% c("Spatial", "Heterogeneity")){
    # Create fig1
    if(sum(is.na(sp_object$sp1))==0){
      fig_fig1 <- convert_col(
        data = sp_object$sp1,
        breaks = breaks,
        pal_fun = CScale,
        right = TRUE,
        include.lowest = FALSE,
        na.col = NA
      )

      fig_values1 <- fig_fig1$colors[which(fig_fig1$tags %in% cut(dplyr::pull(sp_object, sp1),  breaks=breaks))]

      fig1 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=cut(sp1,  breaks=breaks)), colour=col_frontiers) +
        geom_sf(aes(), fill=fig_fig1$fill_by, colour=col_frontiers) +
        ggtitle(title1, subtitle = ifelse(sd_sp1 < sp_null, paste0("Standard Deviation = ", sd_sp1, "*"), paste0("Standard Deviation = ", sd_sp1))) +
        scale_fill_manual(values = fig_values1, name=scale_name) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= ifelse(sd_sp1 < sp_null, "red", "grey13"), hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }else{
      fig1 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=sp1), colour=col_frontiers) +
        scale_fill_manual(name=scale_name) +
        ggtitle(title1, subtitle = paste0("No Effect")) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= "red", hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }


    # Create fig2
    if(sum(is.na(sp_object$sp2))==0){
      fig_fig2 <- convert_col(
        data = sp_object$sp2,
        breaks = breaks,
        pal_fun = CScale,
        right = TRUE,
        include.lowest = FALSE,
        na.col = NA
      )

      fig_values2 <- fig_fig2$colors[which(fig_fig2$tags %in% cut(dplyr::pull(sp_object, sp2),  breaks=breaks))]

      fig2 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=cut(sp2,  breaks=breaks)), colour=col_frontiers) +
        geom_sf(aes(), fill=fig_fig2$fill_by, colour=col_frontiers) +
        ggtitle(title2, subtitle = ifelse(sd_sp2 < sp_null, paste0("Standard Deviation = ", sd_sp2, "*"), paste0("Standard Deviation = ", sd_sp2))) +
        scale_fill_manual(values = fig_values2, name=scale_name) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= ifelse(sd_sp2 < sp_null, "red", "grey13"), hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }else{
      fig2 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=sp2), colour=col_frontiers) +
        scale_fill_manual(name=scale_name) +
        ggtitle(title2, subtitle = paste0("No Effect")) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= "red", hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }

    # Create fig3
    if(sum(is.na(sp_object$sp3))==0){
      fig_fig3 <- convert_col(
        data = sp_object$sp3,
        breaks = breaks,
        pal_fun = CScale,
        right = TRUE,
        include.lowest = FALSE,
        na.col = NA
      )

      fig_values3 <- fig_fig3$colors[which(fig_fig3$tags %in% cut(dplyr::pull(sp_object, sp3),  breaks=breaks))]

      fig3 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=cut(sp3,  breaks=breaks)), colour=col_frontiers) +
        geom_sf(aes(), fill=fig_fig3$fill_by, colour=col_frontiers) +
        ggtitle(title3, subtitle = ifelse(sd_sp3 < sp_null, paste0("Standard Deviation = ", sd_sp3, "*"), paste0("Standard Deviation = ", sd_sp3))) +
        scale_fill_manual(values = fig_values3, name=scale_name) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= ifelse(sd_sp3 < sp_null, "red", "grey13"), hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }else{
      fig3 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=sp3), colour=col_frontiers) +
        scale_fill_manual(name=scale_name) +
        ggtitle(title3, subtitle = paste0("No Effect")) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= "red", hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }

    # Create fig4
    if(sum(is.na(sp_object$sp4))==0){
      fig_fig4 <- convert_col(
        data = sp_object$sp4,
        breaks = breaks,
        pal_fun = CScale,
        right = TRUE,
        include.lowest = FALSE,
        na.col = NA
      )

      fig_values4 <- fig_fig4$colors[which(fig_fig4$tags %in% cut(dplyr::pull(sp_object, sp4),  breaks=breaks))]

      fig4 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=cut(sp4,  breaks=breaks)), colour=col_frontiers) +
        geom_sf(aes(), fill=fig_fig4$fill_by, colour=col_frontiers) +
        ggtitle(title4, subtitle = ifelse(sd_sp4 < sp_null, paste0("Standard Deviation = ", sd_sp4, "*"), paste0("Standard Deviation = ", sd_sp4))) +
        scale_fill_manual(values = fig_values4, name=scale_name) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= ifelse(sd_sp4 < sp_null, "red", "grey13"), hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }else{
      fig4 <- ggplot2::ggplot(data=sp_object) +
        geom_sf(aes(fill=sp4), colour=col_frontiers) +
        scale_fill_manual(name=scale_name) +
        ggtitle(title4, subtitle = paste0("No Effect")) +
        theme(
          plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
          plot.subtitle = element_text(size=11, face= "bold", colour= "red", hjust = 0),
          axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
          axis.text.y=element_blank(), axis.ticks.y=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(0.75, "cm"),
          strip.text.x = element_text(size = 8, face = "bold.italic"),
          legend.position = legend.position
        )
    }
  }else if(fill_by == "RR"){
    # Create fig1
    fig_fig1 <- convert_col(
      data = sp_object$sp1,
      breaks = breaks,
      pal_fun = CScale,
      right = TRUE,
      include.lowest = FALSE,
      na.col = NA
    )

    fig_values1 <- fig_fig1$colors[which(fig_fig1$tags %in% cut(dplyr::pull(sp_object, sp1),  breaks=breaks))]

    fig1 <- ggplot2::ggplot(data=sp_object) +
      geom_sf(aes(fill=cut(sp1,  breaks=breaks)), colour=col_frontiers) +
      geom_sf(aes(), fill=fig_fig1$fill_by, colour=col_frontiers) +
      ggtitle(title1, subtitle = groups_names[1]) +
      scale_fill_manual(values = fig_values1, name=scale_name) +
      theme(
        plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
        plot.subtitle = element_text(size=11, face= "bold", colour= "grey13", hjust = 0),
        axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        legend.text = element_text(size = 12),
        legend.key.size = unit(0.75, "cm"),
        strip.text.x = element_text(size = 8, face = "bold.italic"),
        legend.position = legend.position
      )

    # Create fig2
    fig_fig2 <- convert_col(
      data = sp_object$sp2,
      breaks = breaks,
      pal_fun = CScale,
      right = TRUE,
      include.lowest = FALSE,
      na.col = NA
    )

    fig_values2 <- fig_fig2$colors[which(fig_fig2$tags %in% cut(dplyr::pull(sp_object, sp2),  breaks=breaks))]

    fig2 <- ggplot2::ggplot(data=sp_object) +
      geom_sf(aes(fill=cut(sp2,  breaks=breaks)), colour=col_frontiers) +
      geom_sf(aes(), fill=fig_fig2$fill_by, colour=col_frontiers) +
      ggtitle(title2, subtitle = groups_names[2]) +
      scale_fill_manual(values = fig_values2, name=scale_name) +
      theme(
        plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
        plot.subtitle = element_text(size=11, face= "bold", colour= "grey13", hjust = 0),
        axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        legend.text = element_text(size = 12),
        legend.key.size = unit(0.75, "cm"),
        strip.text.x = element_text(size = 8, face = "bold.italic"),
        legend.position = legend.position
      )

    # Create fig3
    fig_fig3 <- convert_col(
      data = sp_object$sp3,
      breaks = breaks,
      pal_fun = CScale,
      right = TRUE,
      include.lowest = FALSE,
      na.col = NA
    )

    fig_values3 <- fig_fig3$colors[which(fig_fig3$tags %in% cut(dplyr::pull(sp_object, sp3),  breaks=breaks))]

    fig3 <- ggplot2::ggplot(data=sp_object) +
      geom_sf(aes(fill=cut(sp3,  breaks=breaks)), colour=col_frontiers) +
      geom_sf(aes(), fill=fig_fig3$fill_by, colour=col_frontiers) +
      ggtitle(title3, subtitle = groups_names[3]) +
      scale_fill_manual(values = fig_values3, name=scale_name) +
      theme(
        plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
        plot.subtitle = element_text(size=11, face= "bold", colour= "grey13", hjust = 0),
        axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        legend.text = element_text(size = 12),
        legend.key.size = unit(0.75, "cm"),
        strip.text.x = element_text(size = 8, face = "bold.italic"),
        legend.position = legend.position
      )

    # Create fig4
    fig_fig4 <- convert_col(
      data = sp_object$sp4,
      breaks = breaks,
      pal_fun = CScale,
      right = TRUE,
      include.lowest = FALSE,
      na.col = NA
    )

    fig_values4 <- fig_fig4$colors[which(fig_fig4$tags %in% cut(dplyr::pull(sp_object, sp4),  breaks=breaks))]

    fig4 <- ggplot2::ggplot(data=sp_object) +
      geom_sf(aes(fill=cut(sp4,  breaks=breaks)), colour=col_frontiers) +
      geom_sf(aes(), fill=fig_fig4$fill_by, colour=col_frontiers) +
      ggtitle(title4, subtitle = groups_names[4]) +
      scale_fill_manual(values = fig_values4, name=scale_name) +
      theme(
        plot.title = element_text(size=14, face= "bold", colour= "black", hjust = 0),
        plot.subtitle = element_text(size=11, face= "bold", colour= "grey13", hjust = 0),
        axis.text.x=element_blank(),  axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank(),
        legend.text = element_text(size = 12),
        legend.key.size = unit(0.75, "cm"),
        strip.text.x = element_text(size = 8, face = "bold.italic"),
        legend.position = legend.position
      )
  }

  # Create final figure
  gridExtra::grid.arrange(fig1, fig2, fig3, fig4, ncol=ncol_fig)
}
```


```{r chunk5, eval=FALSE}
plot.SpANOVA(
  obj=ResMod,
  obj_type="SpANOVA",
  fill_by="Spatial",
  n_mod=20,
  sp_object=sp_object_sim,
  breaks=c(-3, -2, -1, -0.5, -0.1, 0.1, 0.5, 1, 2, 3),
  fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
  scale_name="Values",
  sp_null=0.125,
  legend.position="right",
  ncol_fig=2
)
```

As well as the adjusted relative risks:

```{r chunk6, eval=FALSE}
INLA.SocialEp::plot.SpANOVA(
  obj=ResMod,
  obj_type="SpANOVA",
  fill_by="RR",
  n_mod=20,
  sp_object=sp_object_sim,
  breaks=c(0, 0.5, 0.9, 1.1, 2, 3),
  fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
  scale_name="Values",
  sp_null=0.125,
  legend.position="right",
  ncol_fig=2
)
```

***
