---
title: "Usage Example"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Usage Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<div style="text-align: justify">

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
install.packages("INLA", repos=c(getOption("repos"), INLA="https://inla.r-inla-download.org/R/stable"), dep=TRUE)
library("dplyr")
library("ggplot2")
```

# Introduction

```{r}
library("INLA.SocialEp")
```

# Understanding the inputs

First of all, the user needs to prepare a graph from an sf object using the following functions from packages *spdep* and *INLA*:

```{r}
sec.nb <- spdep::poly2nb(sp_object_sim, snap=0.0000005)
spdep::nb2INLA("MapGraph", sec.nb)
graph_states <- INLA::inla.read.graph("MapGraph")
```

Next, the user needs to make sure the data has the proper format. Specifically, data for the model needs to be a data.frame that has the following structure:

  * **obs**: contains the observations for the response variable per area and group.
  * **exp**: contains the expected values per area and group.
  * **lev.fac1**: contains the levels of *factor 1* per area and group.
  * **lev.fac2**: contains the levels of *factor 2* per area and group.

```{r}
data_mod <- data.frame(
  "obs" = c(sp_object_sim$OBS_M6_SIM_G1_v3, sp_object_sim$OBS_M6_SIM_G2_v3, 
            sp_object_sim$OBS_M6_SIM_G3_v3, sp_object_sim$OBS_M6_SIM_G4_v3),
  "exp" = c(sp_object_sim$EXP, sp_object_sim$EXP, sp_object_sim$EXP, sp_object_sim$EXP),
  "lev.fac1" = c(rep("F1L1", graph_states$n*2), rep("F1L2", graph_states$n*2)), 
  "lev.fac2" = c(rep("F2L1", graph_states$n), rep("F2L2", graph_states$n), rep("F2L1", graph_states$n), rep("F2L2", graph_states$n))
)
```

Moreover, the user needs to specify the following arguments:

  * **gr**: graph for the underlying spatial structure generated using the function `inla.read.graph()` from the INLA package.
  * **fac.names**: name of the factors, with the format `c("F1", "F2")`.
  * **lev.fac1**: name of the levels of factor 1, with the format `c("F1L1", "F1L2")`.
  * **lev.fac2**: name of the levels of factor 2, with the format `c("F2L1", "F2L2")`.
  * **thres**: threshold used to consider a spatial effect as spurious, default is $0.125$.
  * **verbose.INLA**: option to run INLA with `verbose=TRUE` if the user wants to do debugging on the models, default is *FALSE*.

# Customizing parameters

There are three mainly aspects regarding the modelization and post-processing that can be modified by the user:

  * **Prior Specification**: the function allows the user to choose between uniform prior (`sp.prior = "pc.prec"`) or Penalized-Complexity priors (`sp.prior = "pc.prec"`), with the user being able to modify the paremeters of the PC prior using option `pc.prec.val = c(1, 0.01)`.
  * **Shared Copies in INLA**: you can control if you want the shared copies to be fixed with option `sp.copy.fixed=TRUE`.
  * **Scaled Spatial Effects**: this option controls whether the random spatial effects have their variance scaled (`scale.mod=TRUE`) or not (`scale.mod=FALSE`).

Lastly, the user can specify several options that determine which parts of the INLA models are saved in the final object. Particularly, the user has the following options:
  
  * **save.res**: save residuals from the different models, default is *FALSE*.
  * **save.random**: save random spatial effects from the different models, default is *TRUE*.
  * **save.fixed**: save fixed effects from the different models, default is *TRUE*.
  * **save.hyper**: save hyperparameters data from the different models, default is *TRUE*.
  * **save.mod.data**: save data to rerun the model later using INLA function directly, default is *FALSE*.

```{r chunk2}
ResMod <- INLA.SocialEp::inla.SpANOVA.2x2(
  data = data_mod,
  gr = graph_states,
  fac.names = c("F1", "F2"),
  lev.fac1 = c("F1L1", "F1L2"),
  lev.fac2 = c("F2L1", "F2L2"),
  scale.mod = FALSE,
  sp.prior = "pc.prec",
  pc.prec.val = c(1, 0.01),
  sp.copy.fixed = FALSE,
  save.res=FALSE, 
  save.random=FALSE,
  save.hyper=FALSE, 
  save.mod.data=TRUE
  )
```

The object generated by the function contains a **Summary** with the results of the different models, which can be easily accessed by doing `object$Summary`:

```{r chunk4}
ResMod$Summary
```

If the user chose the option `save.random=TRUE`, then the different spatial effects adjusted can be accessed and plotted. Package includes the `plotSpANOVA()` function, allowing the user to easily plot both the spatial effects and the relative risks adjusted. For example, we could plot the spatial effect for model number 20 using the following code:

```{r chunk5, eval=FALSE}
INLA.SocialEp::plotSpANOVA(
  obj=ResMod,
  obj_type="SpANOVA",
  fill_by="Spatial",
  n_mod=20,
  sp_obj=sp_object_sim,
  fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
  scale_name="Values",
  sp_null=0.125,
  legend.position="right",
  ncol_fig=2
)
```

Moreover, if the user wanted to plot the relative risks adjusted for that same model, we could use the following code:

```{r chunk6, eval=FALSE}
INLA.SocialEp::plotSpANOVA(
  obj=ResMod,
  obj_type="SpANOVA",
  fill_by="RR",
  n_mod=20,
  sp_obj=sp_object_sim,
  fil_scale=c("#133BF2", "#7189F7", "#FFFFFF", "#FF867A", "#FF2F1B"),
  scale_name="Values",
  sp_null=0.125,
  legend.position="right",
  ncol_fig=2
)
```

***
